First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-05-10 eg6-letters/coherent/dvcs_he4_prl.tex
eg6-letters/coherent:  implement Carmans comments, part B

The CEBAF Large Acceptance Spectrometer (CLAS) in Hall B at Jefferson Lab has been
previously supplemented with an inner calorimeter (IC) and a solenoid magnet to
measure DVCS observables on the nucleon
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}. The IC 
extended the photon detection acceptance of CLAS to polar angles as low as 
4$^{\circ}$. The 5 T solenoid magnet acted as a guiding field for the 
low-energy M\o{}ller electrons that were absorbed in a  
heavy shield placed around the beam line.

>>>>

The CEBAF Large Acceptance Spectrometer (CLAS) in Hall B at Jefferson Lab ~\cite{Mecking:2003zu} has been
previously supplemented with an inner calorimeter (IC) and a solenoid magnet to
measure DVCS observables on the nucleon
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}. The IC 
extended the photon detection acceptance of CLAS to polar angles as low as 
4$^{\circ}$. The 5 T solenoid magnet acted as a guiding field for the 
low-energy M\o{}ller electrons that were absorbed in a  
heavy shield placed around the beam line.
